\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-09 fully-abstract-comp/popl2019/paper.tex
Formatting of FTLR, so it takes up less space.

\begin{lemma}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If
  \begin{itemize}
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{itemize}
  \item \begin{itemize}
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $({((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps.
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \end{itemize}
  \end{itemize}
  Then
  \[
    \npair{\left(\arraycolsep=0pt\array{l}((\rx,\normal),\baddr,\eaddr,\aaddr),\\
      ((\rx,\normal),\baddr,\eaddr,\aaddr)\endarray\right)} \in \lre(W)
  \]
\end{lemma}

>>>>

\begin{lemma}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$
  and either $[\baddr,\eaddr] \subseteq \ta$ and $({((\rx,\normal),\baddr,\eaddr,\aaddr)}$ behaves reasonably up to $n$ steps or
$[\baddr,\eaddr] \mathrel{\#} \ta$,
then 
  \[
    \npair{\left(((\rx,\normal),\baddr,\eaddr,\aaddr),
      ((\rx,\normal),\baddr,\eaddr,\aaddr)\right)} \in \lre(W)
  \]
\end{lemma}
